Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009] we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too as shows this table:

@@

Another interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was slightly different. They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes. We believe there is a more widely spread systematic effect of educational features.

>>>>

Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009] we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too as this table shows :

@@

The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey lead us to give up on this. But we still think that should be included in a future research on that topic.

Of course, we also looked into other studies connecting educational features and entrepreneurship. As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy ??????? Boyd and Vosikis MAIN BIB ??????????? . One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was still not directly in lign with our research design. They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes. We believe there is a more widely spread systematic effect of educational features.
